Machine learning high multiplicity matrix elements for electron-positron and hadron-hadron colliders

### 2023-03-13 paper2.tex
chapter 6 parameters

Generated phase-space points are fed to {\MadGraph} \cite{Alwall:2014hca,Hirschi:2011pa}
to compute the tree-level and one-loop level matrix elements.
For each phase-space point, we use the corresponding
renormalisation scale sampled and evaluate the strong coupling
constant at this scale using the NNPDF-4.0 NNLO PDF set
\cite{NNPDF:2021njg} with the LHAPDF6 interface \cite{Buckley:2014ana}.
All external particles are treated as massless and $m_{Z} = 91.188$ GeV.

>>>>

Generated phase-space points are fed to {\MadGraph} \cite{Alwall:2014hca,Hirschi:2011pa}
to compute the tree-level and one-loop level matrix elements.
For each phase-space point, we use the corresponding
renormalisation scale sampled and evaluate the strong coupling
constant at this scale using the NNPDF-4.0 NNLO PDF set
\cite{NNPDF:2021njg} with the LHAPDF6 interface \cite{Buckley:2014ana}.
The full set of parameters used to evaluate the matrix elements are
quoted in Table~\ref{table:fame2_params}.
\begin{table}[ht]
    \centering
    \begin{tabular}{ll}
        \toprule
        Parameters & \\
        \midrule
        Scales & \makecell[l]{$\mu_{R}$ sampled logarithmically in range [$\log(\sqrt{s_{\text{com}}}/4)$, $\log(4\sqrt{s_{\text{com}}})$]} \\
        \midrule
        Masses & \makecell[l]{$m_{b} = 4.7$ GeV \\ $m_{t} = 173$ GeV \\ $m_{\tau} = 1.777$ GeV \\ $m_{Z} = 91.188$ GeV \\ $m_{W} = 80.419$ GeV \\ $m_{H} = 125$ GeV} \\
        \midrule
        Couplings & \makecell[l]{$\alpha_{s} = \alpha_{s}(\mu_{R}^{2})$ \\ $\alpha_{e} = 1/132.507$ \\ $G_{F} = 1.166390 \times 10 ^{-5}$ GeV$^{-2}$} \\
        \midrule
        Decay widths & \makecell[l]{$\Gamma_{t} = 1.4915$ GeV \\ $\Gamma_{Z} = 2.441404$ GeV \\ $\Gamma_{W} = 2.0467$ GeV \\ $\Gamma_{H} = 6.382339 \times 10^{-3}$ GeV} \\
        \bottomrule
        \end{tabular}
    \caption{List of parameters for the matrix element generation. Masses and decay widths not listed explicitly have been set to zero.}
    \label{table:fame2_params}
\end{table}
